%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Adaptive AutoSAR Engineer} % Job title
    {BA Techworks Inc.} % Organization
    {Nanjing, RPC} % Location
    {May. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design an adaptive AutoSAR application on mPAD, implementation OTA functionality, with GNU/Linux gcc and QNX qcc on Intel x86 platform}
        \item {Define necessary new interfaces, re-use current interfaces, by xxxxxxxx modeling tools and AutoSAR toolchains}
        \item {Design ITF and SCTF test cases by pytest tools and integraded into bazel rules}
        \item {Support integration test activity on test rack and on vehicle, investigate behaviors between different modules, including Xx, XxxX, XXXX, etc}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedded Engineer} % Job title
    {BYTON Ltd} % Organization
    {Nanjing, RPC} % Location
    {Dec. 2018 - May. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and delivery of gateway features including but not limited to CAN logging, CAN/ETH routing, diagnostic. GNU/Linux with C++ on ARMv8}
        \item {Design of CAN log parser front end using JavaScript React}
        \item {Design of dual partition upgrade functionality, based on u-boot and swupdate, on Xilinx ZCU102 platform.}
        \item {Prototyping iOS app to remote control vehicle}
        \item {Define and interfaces between telematics and FIC/BCM/DCM/ADAS, including but not limited to CAN Matrix,DBC,UDS}
        \item {Design of keyless entry features, including off-chip OTA upgrade, low-voltage detection, BLE characteristic for vehicle, using TI SimpleLink CC26x2 SDK}
        \item {Support Xilinx BSP configuration and integration, on Xilinx ZCU102 platform.}
        \item {Support cross-compilation toolchain configuration and integration control commands, erase/re-pair, discovery. using TI SimpleLink CC26x2 SDK}
        \item {Support customize verification procedure and firmware for manufacturing}
        \item {Support design of Android App for passive BLE scan, log transferring, whitelist modification, etc}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Product Owner \& Line Manager} % Job title
    {CIeNET Technologies, Inc.} % Organization
    {Nanjing, PRC} % Location
    {Oct. 2015 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managing and leading 2 XFT teams for track maintenance}
        \item {Managing and leading 1 XFT teams for eDRX feature defined in 3GPP TS 45.008, embedded C developing on PowerPC platform, targeting reducing the power consumer of Raido Base Station}
        \item {Managing and leading 1 XFT teams for EC-GSM feature defined in 3GPP TS 45.008, embedded C developing on PowerPC platform, targeting extending cellular network coverage without hardware investment}
        \item {Managing and leading 1 XFT teams for Continuous Integration workflow, including but not limited to equipment interface abstraction, resource allocation and configuraiton framework, etc}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedded Designer} % Job title
    {Lucent Technologies, Inc.} % Organization
    {Nanjing, PRC} % Location
    {May. 2004 - Oct. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implement sync mechanism between heterogeneous nodes of core network}
        \item {Granularity improvement on performance count features}
        \item {Deployment of network management system}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
